
\documentclass[a4paper,10pt]{article}
\input{../preamble}

\begin{document}

%----------HEADER----------
\cvheader

\section{Executive Summary}
Passionate about Data Science and Statistical Analysis, with growing  experience in R, Python, SQL, Power BI, and Excel. Enjoy working on data-driven problems, statistical modeling,
and building dashboards that support better decision-making.

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheadingLink
{Universitas Gadjah Mada}{Sleman, Special Region of Yogyakarta}
{Bachelor of Statistics, 3.81/4.00}{Aug 2022 -- Apr 2026}{https://drive.google.com/drive/folders/1YOaojBjWkupV8UFNj4842qaEr87SnfP6?usp=drive_link}
\resumeItemListStart
\resumeItem{Dual Scholarship Awardee: Dato' Low Tuck Kwong - Aktivis Scholarship 2024 (for leadership in student data science initiatives, academic excellence, and contributions to the UGM student community) | BSI Scholarship Talenta 2025 (for intensive career preparation, leadership development, and mentorship programs).}
\resumeItem{Achieved multiple top rankings in national-level competitions in statistics, data analysis, and data visualization.}
\resumeItemListEnd

\resumeSubheadingLink
{Coding Camp powered by DBS Foundation}{Remote}
{Machine Learning Engineer Cohort}{Feb 2025 -- Jun 2025}{https://drive.google.com/drive/folders/1W4UkeeFqUC0RiaXonMnGKAPj1j4o6yA1?usp=drive_link}
\resumeItemListStart
\resumeItem{Mastered material through 5+ independent tasks and 1 capstone projects, participated in 7+ live sessions for soft skills, english proficiency, study groups, and received mentorship to enhance learning.}
\resumeItem{Collaborated with a 6-member cross-functional team (Machine Learning \& Front-End Back-End) on a national capstone project: developed a web app for digital fraud prevention and built a model to detect suspicious URLs.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheadingLink
{PT Bina Pertiwi (Member of Astra)}{East Jakarta, Special Region of Jakarta}
{Data Analyst Intern}{Mar 2025 -- Jun 2025}{https://ugm.ac.id}
\resumeItemListStart
\resumeItem{Collected, preprocessed, analyzed, and managed 4+ national-level data, including historical training data, employee competency \& grade data, and asset databases.}
\resumeItem{Developed real-time dashboard using Google Data Studio  with 4+ sections aligned with each data source to support informed decision-making.}
\resumeItem{Collaborated with team members to provide actionable insights and data-driven recommendations.}
\resumeItemListEnd

\resumeSubheading
{Cortex Data Indonesia}{Remote}
{Social Research and Data Solution Intern}{Jul 2024}
\resumeItemListStart
\resumeItem{Implemented web scraping techniques using BeautifulSoup, extracting and processing 2+ data to improve data accessibility for analysis.}
\resumeItem{Deployed a web application for classifying nitrogen deficiency in rice plants using Streamlit, utilizing open-source code available on another contributor's GitHub repository.}
\resumeItem{Collaborated on the 2 research proposal, contributing to analytical methodologies that improved research feasibility, strategic planning, and clarity of research objectives.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------ORGANIZATIONAL EXPERIENCE-----------
\section{Organizational Experience}
\resumeSubHeadingListStart

\resumeSubheadingLink
{Komunitas Mahasiswa Satria Data Universitas Gadjah Mada}{}
{President}{Jan 2024 -- Dec 2024}{https://drive.google.com/drive/folders/1LcFSk7ZtGxcoOUBqmhth_Z5IxuEAjmg8?usp=drive_link}
\resumeItemListStart
\resumeItem{Successfully led Universitas Gadjah Mada to achieve 4th place in the overall championship of Satria Data 2024, strengthening the university's presence in national-level data competitions.}
\resumeItem{Led a 27-member team, improving collaboration efficiency and achieving key milestones.}
\resumeItem{Led internal meetings \& built partnerships with university stakeholders, improving communication \& expanding community initiatives.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS, ACHIEVEMENTS, INTEREST & SKILLS-----------
\section{Projects, Achievements, Interest, \& Skills}

\resumeInfoLink{Projects}{Interactive Dashboard Development – Built Google Data Studio dashboards for business insights | Statistical Data Infographics – Created 2 visual reports using Python, R, Canva \& Illustrator, achieving top 2 national competition | Research Papers (Competition \& Course Projects) – Conducted statistical analysis (SPSS, Minitab, WarpPLS, R, Python, SPSS, Minitab, E Views) with findings applied in 5 national competitions | Detailed project documentation available on GitHub.}{https://drive.google.com/drive/folders/1ERN0xRSXTLrEPZVhUqZ6dFuVn-3NOrPy?usp=drive_link}

\resumeInfoLink{Achievements} {2nd Place – Statistics Infographic Competition, Satria Data 2023 (Ministry of Education, Culture, Research, and Technology) | 3rd Place – Statistics Olympiad, RASIO 8.0 2024 (Statistics Student Association, Universitas Padjadjaran) | 1st Place – Data Analysis Competition, National Statistics Challenge 2024 (Statistics Student Association, Universitas Brawijaya) | 1st Place – Data Analytics Competition, Acavero 2024 (Information Systems Student Association, Telkom University) | Top 5 Finalist – Diponegoro Statistics Olympiad, Dokter Data 2024 (Statistics Student Association, Universitas Diponegoro) | Best Presentation (Top 6 Finalist) – Olimpiade Nasional Statistika, ANAVA \#19 2025 (Statistics Student Association, Universitas Gadjah Mada).}{https://drive.google.com/drive/folders/1YOaojBjWkupV8UFNj4842qaEr87SnfP6?usp=drive_link}

\resumeInfo{Interest} {Data Analytics \& Science | Data
  Visualization \& Interactive Dashboard Development | Statistical Modeling \& Risk Analysis | Computational Programming (R, Python, SQL) | Economic Statistics \& Time Series Forecasting.}

\resumeInfo{Soft Skills} {Problem-Solving \& Critical Thinking | Attention to Detail \& Professional Ethics | Adaptability \& Deadline Management | Collaboration \& Teamwork | Effective Communication | Data Storytelling.}

\resumeInfo{Hard Skills} {Data Acquisition, Wrangling, \& Processing (SQL, Python) | Statistical Analysis, Machine Learning, \& Modeling (Classification, Regression, Clustering, Time Series Forecasting) using R, Python, SPSS, Minitab, EViews | Data Visualization \& Business Intelligence (Google Data Studio, Microsoft Power BI) \& Infographic Design (Canva) | Scientific, Technical, \& Analytical Report Writing.}

\resumeInfoLink{Certifications} {Belajar Dasar Git dengan GitHub | Belajar Dasar Visualisasi Data | Belajar Dasar Structured Query Language (SQL) | Belajar Analisis Data dengan Python | Belajar Pengembangan Machine Learning | (Dicoding Indonesia).}{https://www.dicoding.com/users/fahmidza/academies}

\resumeInfoLink{Languages} {Indonesian (Native) | English (Professional Working Proficiency – TOEFL ITP Prediction Score: 463, Schoters, Oct 2025).}{https://drive.google.com/drive/folders/1J4LxUS6u9l3BttCQ8wPOalpvrgZIaO6A?usp=sharing}


\end{document}